What We Eval in the Shadows

### 2021-04-16 paper/main.tex
Updates

  \item \emph{Block \c{(BLOCK)}} can appear anywhere, but it is almost always
    the case that the block is only passed to \eval rather than being directly
    part of in as in \c{eval({...})}. Essentially, the block denotes a fragment
    of a program to be evaluated in a special way. There is a number of use
    cases: unit testing frameworks (\eg \c{testthat}, \c{testit}), code
    benchmarking (\eg \c{rbenchmark}, \c{microbenchmark}), running code in
    parallel (\eg \c{foreach}, \c{doParallel}), or deferring code execution
    (\eg \c{withr}).

  \item \emph{Simple function calls \c{(F())}}

  \item \emph{Complex function calls \c{(F(X), F(F(X)))}}

>>>>

  \item \emph{Function calls \c{(F(), F(X), F(F(X)))}}

  \item \emph{Block \c{(BLOCK)}} can appear anywhere, but it is almost always
    the case that the block is only passed to \eval rather than being directly
    part of in as in \lstinline|eval({...})|. Essentially, the block denotes a fragment
    of a program to be evaluated in a special way. There is a number of use
    cases: unit testing frameworks (\eg \c{testthat}, \c{testit}), code
    benchmarking (\eg \c{rbenchmark}, \c{microbenchmark}), running code in
    parallel (\eg \c{foreach}, \c{doParallel}), or deferring code execution
    (\eg \c{withr}).
